We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-01 paper/paper.tex
+1 paragraph

The midle panel

>>>>

The middle panel shows the LG compared against the results from
Illustris. In this case we find a similar trend. The MW is atypical
and M31 is within the variance from the simulation data.
This time, however, there is a single MW-like galaxy out of the total
of 20 that shows an $c/a$ as small as the MW.
The only assymetry evident between the simulated halos is in the
dispersion, the $c/a$ distribution for the massive halos seems to be
wider than it is for the less massive partner.
